Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-03-31 ch04-lrmhinf/ch04appendices.inc.tex
Some cleanup

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function that is implemented as a discrete state-space model.
This controller was present beforehand~\citep{Rademakers2005MSc,vanderMaas2011MSc} and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef \stateSpace{A}{B}{C}{D}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are shared among the translational directions and the rotational direction respectively.

\TODO{show bode plot of controller directions}

@@

The $6$ velocity signals that are read from the Q8 \gls{DAQ} are each filtered to \TODO{filtered such that what?} using a filter  $F$ with transfer function
\begin{equation}
  F(s) \approx \input{\thisDir/data/avis-setup/sensor-filter.inc.tex}
  \text{.}
\end{equation}
This filter is discretized automatically by \Simulink for the actual implementation, which obviously happens in discrete time.
\TODO{show bode plot of $F$}
The output \code{y} is clipped to $\pm 20$ for easier detection of errors.
However, during normal operation and all the measurements, the signal levels were well within the linear region of this saturation block.

>>>>

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function that is implemented as a discrete state-space model.
This controller was present beforehand~\citep{Rademakers2005MSc,vanderMaas2011MSc} and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef \stateSpace{A}{B}{C}{D}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are shared among the translational directions and the rotational direction respectively as shown in \figref{fig:avis:bodeplots:controllerAndSensor}.

\begin{figure}
\TODO{show bode plot of controller directions}
\caption{Bode plots of the $\experimental\Controller$ and sensor filter $F$.}
\label{fig:avis:bodeplots:controllerAndSensor}
\end{figure}

@@

The $6$ velocity signals that are read from the Q8 \gls{DAQ} are each filtered to \TODO{filtered such that what?} using a filter  $F$ with transfer function
\begin{equation}
  F(s) \approx \input{\thisDir/data/avis-setup/sensor-filter.inc.tex}
\end{equation}
which is shown in \figref{fig:avis:bodeplots:controllerAndSensor}.
This filter is discretized automatically by \Simulink for the actual implementation, which happens in discrete time.

The output \code{y} is clipped to $\pm 20$ for easier detection of errors.
However, during normal operation and all the measurements, the signal levels were well within the linear region of this saturation block.
